Gusto: a toolkit for compatible finite element dynamical cores

### 2024-08-22 source/paper.tex
latest progress - not happy with it

@@

In this article we will describe the current capabilities of Gusto and
the design features that enable our flexible implementation whereby
different spatial and temporal discretisations can be applied to a
range of different equation sets relevant for weather and climate
modelling. In section \ref{sec: governing} we will outline three
different equations commonly used for modelling geophysical fluids in
order to demonstrate the similaries between the equations and justify
the use of a unified codebase. The advantages of this unified approach
become even clearer in section \ref{sec: FEM} where we present the
compatible finite element discretisation of the different types of
terms (e.g. pressure gradient, transport) seen in section \ref{sec:
  governing}. In section \ref{sec: design} we describe the code
structure of Gusto followed by a detailed example (section \ref{sec:
  FML}) of the Form Manipulation Language (FML) that facilitates
symbolic manipulation of the finite element forms within our
timestepping code. Section \ref{sec: results} contains a selection of
numerical results that showcases the range of discretisations
available within Gusto. **mention here new functionality facilitated
by the flexibility of Gusto? We summarise our current status and
future directions in section \ref{sec: summary}.

@@

\subsubsection{Grids and HDiv elements}

>>>>

Given that there are many promising avenues for research in the area
of compatible finite element discretisations for geophysical fluid
dynamics (**where to say what these are?), a flexible, extensible
implementation of the methods is strongly desirable. This is
especially required because, while it is feasible for someone to write
a code implementing a specific finite element discretisation of a PDE,
the code quickly becomes complicated and unsustainable when
investigating different orders or families of finite elements, or
different formulations of the equation. For geophysical fluid dynamics
applications there are additional considerations relating to the
geometry and types of waves present in the flow. For example, the
scales of motion in the horizontal and vertical directions differ by
several orders of magnitude. (also: boundaries, vertical staggering
for theta space)

@@

In this article we will describe the current capabilities of Gusto and
the design features that enable our flexible implementation whereby
different spatial and temporal discretisations can be applied to a
range of different equation sets relevant for weather and climate
modelling. In section \ref{sec: governing} we will outline three
different equations commonly used for modelling geophysical fluids in
order to demonstrate the similaries between the equations and justify
the use of a unified codebase. The advantages of this unified approach
become even clearer in section \ref{sec: FEM} where we present the
compatible finite element discretisation of the different types of
terms (e.g. pressure gradient, transport, diffusion) seen in section
\ref{sec: governing}. In section \ref{sec: design} we describe the
code structure of Gusto followed by a detailed example (section
\ref{sec: FML}) of the Form Manipulation Language (FML) that
facilitates symbolic manipulation of the finite element forms within
our timestepping code. Section \ref{sec: results} contains a selection
of numerical results that showcases the range of discretisations
available within Gusto. **mention here new functionality facilitated
by the flexibility of Gusto? We summarise our current status and
future directions in section \ref{sec: summary}.

@@

\subsubsection{Grids and finite element families}
